\textsf{Are large language models superhuman chemists?}

### 2024-03-28 src/tex/sections/manually_sources_table.tex
update credits

\begin{table}[h]
    \begin{tabularx}{\textwidth}{p{3.5 cm}p{6.5 cm}p{.5cm}X}
    \toprule
    source & description & question count \\
    \midrule
NMR spectroscopy & Questions are based on images shared via the Twitter account \href{https://twitter.com/NMRspectroscopy}{NMRspectroscopy} && 5 \\
Analytical chemistry & Questions are based on exercises in master student examination at the Friedrich Schiller University, Jena, Germany &&  \variable{output/question_count_per_dir/json_file_counts_analytical_chemistry.txt} \\
\
\multirow{2}{*}{General chemistry} & Questions originate from examinations for grade 10 at the Marist Comprenhensive Academy Uturu, Nigeria && \variable{output/question_count_per_dir/json_file_counts_Gen_Chem_MCA.txt} \\
 & Questions originate from the Bachelor of Science (for chemistry) courses at the Technical University of Munich, Germany && 8 \\
Functional materials and  nanomaterials & Questions are based on exercises in a seminar conducted at the Friedrich Schiller University, Jena, Germany && \variable{output/question_count_per_dir/json_file_counts_func_mats_and_nanomats.txt} \\
Combustion engineering & Based on a Master of Science examination paper at the University of Magdeburg, Germany && \variable{output/question_count_per_dir/json_file_counts_combustion_engineering.txt} \\
Materials' synthesis & Questions are based on seminars on material synthesis from Friedrich Schiller University, Jena, Germany && \variable{output/question_count_per_dir/json_file_counts_materials_synthesis.txt} \\
Chemistry olympiad & National and International Olympiads held in US, UK and Moldova && \variable{output/question_count_per_dir/json_file_counts_icho.txt} \\
Organic reactivity & Based on Bachelor of Science in Chemistry at the Technical University of Munich, Germany && \variable{output/question_count_per_dir/json_file_counts_organic_reactivity.txt} \\
Periodic table & Manually created && \variable{output/question_count_per_dir/json_file_counts_periodic_table_properties.txt} \\
Polymer chemistry & Based on examinations at the University of Hamburg, Germany && \variable{output/question_count_per_dir/json_file_counts_polymer_chemistry.txt} \\
Textbook questions & Various textbooks covering biomolecular science, drug synthesis, molecular structure, organic chemistry, and X-ray crystallography && \variable{output/question_count_per_dir/json_file_counts_oup.txt} \\
Safety & Based on the question bank published by the Federal/State Working Group  on Chemical Safety (BLAC), which is used for the expertise examination (“Sachkundeprufung”) && \variable{output/question_count_per_dir/json_file_counts_blac_gfk.txt} \\
\bottomrule
\end{tabularx}
\end{table}

>>>>

\begin{table}[h]
    \begin{tabularx}{\textwidth}{p{3.5 cm}p{6.5 cm}p{.5cm}X}
    \toprule
    source & description & question count \\
    \midrule
NMR spectroscopy & Questions are based on images shared via the Twitter account \href{https://twitter.com/NMRspectroscopy}{NMRspectroscopy} && 5 \\
\midrule
Analytical chemistry & Questions are based on exercises in master student examination at the Friedrich Schiller University, Jena, Germany &&  \variable{output/question_count_per_dir/json_file_counts_analytical_chemistry.txt} \\
\midrule
\multirow{2}{*}{General chemistry} & Questions originate from examinations for grade 10 at the Marist Comprenhensive Academy Uturu, Nigeria && \variable{output/question_count_per_dir/json_file_counts_Gen_Chem_MCA.txt} \\
 & Questions originate from the Bachelor of Science (for chemistry) courses at the Technical University of Munich, Germany && 8 \\
 \midrule
Functional materials and  nanomaterials & Questions are based on exercises in a seminar conducted at the Friedrich Schiller University, Jena, Germany && \variable{output/question_count_per_dir/json_file_counts_func_mats_and_nanomats.txt} \\
\midrule
Combustion engineering & Based on a Master of Science examination paper at the University of Magdeburg, Germany && \variable{output/question_count_per_dir/json_file_counts_combustion_engineering.txt} \\
\midrule
Materials' synthesis & Questions are based on seminars on material synthesis from Friedrich Schiller University, Jena, Germany && \variable{output/question_count_per_dir/json_file_counts_materials_synthesis.txt} \\
\midrule
Chemistry olympiad & National and International Olympiads held in US, UK and Moldova && \variable{output/question_count_per_dir/json_file_counts_icho.txt} \\
\midrule
Organic reactivity & Based on exams in the Bachelor of Science in Chemistry at the Technical University of Munich, Germany && \variable{output/question_count_per_dir/json_file_counts_organic_reactivity.txt} \\
\midrule
Periodic table & Manually created && \variable{output/question_count_per_dir/json_file_counts_periodic_table_properties.txt} \\
\midrule
Polymer chemistry & Based on examinations at the University of Hamburg, Germany && \variable{output/question_count_per_dir/json_file_counts_polymer_chemistry.txt} \\
\midrule
Textbook questions & Various textbooks covering biomolecular science, drug synthesis, molecular structure, organic chemistry, and X-ray crystallography && \variable{output/question_count_per_dir/json_file_counts_oup.txt} \\
\midrule
Safety & Based on the question bank published by the Federal/State Working Group  on Chemical Safety (BLAC), which is used for the expertise examination (“Sachkundeprufung”) && \variable{output/question_count_per_dir/json_file_counts_blac_gfk.txt} \\
\bottomrule
\end{tabularx}
\end{table}
